---
title: "Homework 1"
author: Diana Sanchez
output: github_document
---

This is my solution to HW1.

``` {r}
library(tidyverse)
```


## Problem 1

Create a data frame with the specified elements.

```{r}
prob1_df =
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
)
```

Take the mean of each variable in my data frame.

```{r}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logical, but not character or factor variables

```{r}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

I can convert logical and factor variables to numeric variables, but I can't do this for a character variable.

```{r eval = FALSE}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
```

I can convert a logical variable to a numerica and then multiply it by the random sample, but I can't multiply factor variables by the random sample. However, I can convert the logical variable to a factor variable and then to numeric and then multiply by the random sample. However, this gives me a different result compared to converting the logical variable directly to a numeric variable.

## Problem 2

data("penguins", package = "palmerpenguins")
